Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Migration graph characterization

\maciek{Rewrite above paragraph to say that our algorithm is essentially DET from DISC16, with concretised reconfiguration strategy (i.e., the cheapest)}

@@

\noindent
\textbf{Vertices.}
The vertices of the migration graph are all $\ell$ clusters of the instance.
We distinguish the \emph{core vertices} that correspond to clusters directly involved in the merge operation: the clusters containing the to-be-merged components in $C_I$ and the cluster containing the merged component in $C_F$.
There are at most $3$ core vertices in each migration graph (at most two components participate in the merge, and these may migrate to a third cluster).

\noindent
\textbf{Edges and their labels.}

Cost of cluster reconfiguration is the number of exchanged nodes, and from the standpoind of a migration graph, it is the sum of labels on edges of the graph.
It is bounded by $2k$ times the size of the connected component.

Core of the graph and the component merge.

Multiple migration graphs for a component merge exist, and multiple of them might have the optimal cost.
In Section \ref{ssec:cascade}, we show that among all migration graphs for given component merge, there exists an optimal graph with the bounded path length.

>>>>

\maciek{Rewrite above paragraph to say that our algorithm is essentially DET from DISC16, with concretised reconfiguration strategy (i.e., an arbitrary one among the minimum cost reconfigurations)}

@@

\noindent
\textbf{Vertices of the migration graph and the core vertices.}
The vertices of the migration graph are all $\ell$ clusters of the instance.
We distinguish the \emph{core vertices} that correspond to clusters directly involved in the merge operation: the clusters containing the to-be-merged components in $C_I$ and the cluster containing the merged component in $C_F$.
There are at most $3$ core vertices in each migration graph (at most two components participate in the merge, and these may migrate to a third cluster).

\noindent
\textbf{Edges and their labels.}
The edges of the migration graph denote the migration of nodes from $C_I$ to $C_F$.
Each edge is labeled with a number $m$ that denotes the number of migrated nodes between clusters.
Each edge is directed from the cluster that contained the nodes to the cluster they migrated to.
Both edges might exists between a pair of nodes, as whole components of nodes migrate, and the back-and-forth exchange may be needed for the configuration $C_F$ to be component-respecting.

\noindent
\textbf{Vertex degree.}
At most $k$ nodes may migrate from a cluster and at most $k$ nodes may migrate into a cluster.
Thus, the sum of the labels for both ingoing and outgoing edges of each vertex is at most $k$.
This implies that the number of ingoing and outgoing edges is also bounded by $k$.

\noindent
\textbf{Flow preservation.}
In any feasible configuration, each cluster contains exactly $k$ nodes.
Thus, for any vertex, the sum of labels of ingoing edges must equal the sum of labels of outgoing edges.

\noindent
\textbf{Migration graph and the cost of reconfiguration.}
The cost of cluster reconfiguration equals the number of exchanged nodes multiplied by $\alpha$.
From the standpoint of a migration graph, this corresponds to the sum of labels on edges of the graph.
A trivial upper bound on the cost is the size of the connected component in the migration graph multiplied by $2\alpha k$.

Note that for a single component merge, multiple migration graphs may exist, and multiple of them might have the optimal cost.
In Section \ref{ssec:cascade}, we show that among all migration graphs for given component merge, there exists an optimal graph with the bounded path length.
Combined with other properties, this allows to bound the size of the migration graph, and consequently bound the cost of each repartition, that results in a bound of the competitive ratio for \TAlg.
